\chapter{Course Learning Outcomes Alignment}
\label{ch:course}

%-------------------------------------------------------
Summary here if necessary.

\section{Relevance}
Explicitly state how your project meets the relevant Course Learning Outcomes (listed below). Not all projects will cover every outcome, but you should strive to align your project with as many as possible.

Course Learning Outcomes:
\begin{enumerate}
  \item Understanding of Core Concepts
  \begin{itemize}
    \item Explain principles, concepts, methods, techniques, and trends in the fields of data mining and knowledge discovery.
    \item Demonstrate this by providing clear explanations of the methods and algorithms used in your project.
  \end{itemize}
  \item Data Preparation Skills
  \begin{itemize}
    \item Apply transformations to data, including discretization of numeric attributes, numeric coding of nominal attributes, data preprocessing, data cleansing techniques, and selection of appropriate features.
    \item Showcase your data preprocessing steps and justify the techniques used.
  \end{itemize}
  \item Algorithm Implementation (if applicable)
  \begin{itemize}
    \item Apply clustering algorithms (iterative, hierarchical, probability-based, density-based), generate rules by induction, classification rules, and association rules.
    \item Implement appropriate algorithms relevant to your project and explain their application.
  \end{itemize}
  \item Text Mining Proficiency (if applicable)
  \begin{itemize}
    \item Extract knowledge from unstructured text collections and demonstrate the use of sequence mining algorithms to discover patterns across time or positions in a given dataset.
    \item For text mining projects, illustrate how you processed and analyzed textual data to extract meaningful insights.
  \end{itemize}
  \item Evaluation of Results (if applicable)
  \begin{itemize}
    \item Assess the significance of mined frequent patterns and the association rules derived from them by using rule and pattern assessment measures, and employ algorithms to test for the statistical significance of rules and patterns.
    \item Evaluate the results of your analysis using appropriate metrics and discuss their significance.
  \end{itemize}
\end{enumerate}